Approximation as Differentiation notes

### 2025-02-10 notes/definitions.tex
Two different functors..

\noindent Equivalently $\Fam(I,C)$ is the functor category $\Func{I}{C}$ where we interpret $I$ as a discrete
category.

\begin{definition}[Reindexing]
For any $f: I \to J$ define the following contravariant \emph{reindexing} functor $\reindex{-}{f}: \Fam(J,C)
\to \Fam(I,C)$ that sends any $X \in \Fam(J,C)$ to the $I$-indexed family $X[f]$ which has $X[f]_i = X_{f(i)}$
for any $i \in I$.
\end{definition}

>>>>

\noindent Equivalently $\Fam(I,C)$ is the functor category $\Func{I}{C}$ where we interpret $I$ as a discrete
category. $\Fam(-,C): \Set^{\op} \to \Cat$ is a functor which sends any set $I$ to the category $\Fam(I,C)$
and any function $f: I \to J$ to the \emph{reindexing functor} $\reindex{-}{f}: \Fam(J,C) \to \Fam(I,C)$.

\begin{definition}[Reindexing]
For any $f: I \to J$ the \emph{reindexing} functor sends any $J$-indexed family $X$ to the $I$-indexed family
$X[f]$ where $X[f]_i = X_{f(i)}$ for any $i \in I$.
\end{definition}
